Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-07 paper/snakemajoranas.tex
cite Adaptive

\comment{We discretize the Hamiltonian and simulate it with Kwant.}
We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.
To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive. % TODO: add a citation
The entire source code is available in the Supplemental Material~\cite{supp}.  % TODO: update the bib when the data is uploaded
The resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded

>>>>

\comment{We discretize the Hamiltonian and simulate it with Kwant.}
We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
The resulting Hamiltonians are large because instead of having a single slice of sites that is translationally invariant in the $x$-direction, we create a long supercell to make the structure periodic.
To speed up these expensive simulations we employ an adaptive sampling strategy, using the Python package Adaptive.~\cite{adaptive}
The entire source code is available in the Supplemental Material~\cite{supp}.  % TODO: update the bib when the data is uploaded
The resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded
